### 2017-07-20 examples/flights_examples.Rmd
Fix typos
Change from Med to med and sd to sigma

@@

```{r}
fli_small %>%
  specify(response = arr_delay) %>% # alt: arr_delay ~ NULL (or arr_delay ~ 1)
  hypothesize(null = "point", Med = 55) %>%
  generate(reps = params$rep_times, type = "bootstrap") %>%
  calculate(stat = "median", na.rm = TRUE)
```

@@

```{r}
fli_small %>%
  specify(response = arr_delay) %>% # alt: arr_delay ~ NULL (or arr_delay ~ 1)
  hypothesize(null = "point", sd = 40) %>%
  generate(reps = params$rep_times, type = "bootstrap") %>%
  calculate(stat = "sd")
```

@@

```{r}
fli_small %>%
  specify(response = arr_delay) %>% # alt: arr_delay ~ NULL (or arr_delay ~ 1)
  hypothesize(null = "point", sd = 40) %>%
  generate(reps = params$rep_times, type = "bootstrap") %>%
  calculate(stat = "sd", na.rm = TRUE)
```

>>>>

These examples use `r params$num_rows` flights from `nycflights13::flights` and `r params$rep_times` replicates.

@@

```{r}
fli_small %>%
  specify(response = arr_delay) %>% # alt: arr_delay ~ NULL (or arr_delay ~ 1)
  hypothesize(null = "point", med = 55) %>%
  generate(reps = params$rep_times, type = "bootstrap") %>%
  calculate(stat = "median", na.rm = TRUE)
```

@@

```{r}
fli_small %>%
  specify(response = arr_delay) %>% # alt: arr_delay ~ NULL (or arr_delay ~ 1)
  hypothesize(null = "point", sigma = 40) %>%
  generate(reps = params$rep_times, type = "bootstrap") %>%
  calculate(stat = "sd")
```

@@

```{r}
fli_small %>%
  specify(response = arr_delay) %>% # alt: arr_delay ~ NULL (or arr_delay ~ 1)
  hypothesize(null = "point", sigma = 40) %>%
  generate(reps = params$rep_times, type = "bootstrap") %>%
  calculate(stat = "sd", na.rm = TRUE)
```
